Parallel Adaptive Importance Sampling

### 2015-08-17 PAIS.tex
a few suggested edits.

\newcommand{\picturesAB}[6]{
\centerline{
\hskip #4
\raise #3 \hbox{\raise 0.9mm \hbox{(a)}}
\hskip #5
\epsfig{file=#1,height=#3}
\hskip #6
\raise #3 \hbox{\raise 0.9mm \hbox{(b)}}
\hskip #5
\epsfig{file=#2,height=#3}
}}
\newcommand{\picturesCD}[6]{
\centerline{
\hskip #4
\raise #3 \hbox{\raise 0.9mm \hbox{(c)}}
\hskip #5
\epsfig{file=#1,height=#3}
\hskip #6
\raise #3 \hbox{\raise 0.9mm \hbox{(d)}}
\hskip #5
\epsfig{file=#2,height=#3}
}}
\author{Colin Cotter\thanks{Department of Mathematics, Imperial
    College, London, UK} \and Simon Cotter\thanks{School of
    Mathematics, University of Manchester, Manchester, UK. e: simon.cotter@manchester.ac.uk} \and Paul Russell\thanks{School of
    Mathematics, University of Manchester, Manchester, UK}}
\title{Parallel Adaptive Importance Sampling}
\begin{document}
\maketitle
\begin{abstract}
  Markov chain Monte Carlo methods are commonly used and powerful
  family of numerical methods for sampling from complex probability
  distributions. As the applications that these methods are being
  applied to increase in size and complexity, the need for efficient
  methods which can exploit the parallel architectures which are
  prevalent in high performance computing increases. In this paper, we
  aim to develop a framework for scalable parallel MCMC algorithms. At
  each iteration, an importance sampling proposal distribution is
  formed using the current states of all of the chains within an
  ensemble. Once weighted samples have been produced from this, a
  state-of-the-art resampling method is then used to create an evenly
  weighted sample ready for the next iteration. We demonstrate that
  this parallel adaptive importance sampling (PAIS) method outperforms
  naive parallelisation of serial MCMC methods using the same number
  of processors, for low dimensional problems, and in fact shows
  better than linear improvements in convergence rates with respect to
  the number of processors used.
\end{abstract}
\begin{keywords}MCMC, parallel, importance sampling, Bayesian, inverse problems.
\end{keywords}
\section{Introduction}
%\subsection{Lit. review}
%\subsection{Optimal transport resampler}
%\subsection{Function Space MCMC}
Markov chain Monte Carlo (MCMC) methods are a powerful family of tools
that allow us to sample from complex probability distributions. MCMC
methods were first developed in the 70s\cite{hastings1970monte}, and with the development of
faster more powerful computers, have become ever more important in a
whole range of fields in statistics, science and engineering. However,
despite the advances in hardware that have made it possible to fully
characteries the posterior distributions of many problems, it remains
unfeasible to use MCMC methods for many more. In particular, when
considering Bayesian inverse problems, each MCMC step may involve the
numerical solution of one or more PDE. As many samples are usually
required before Monte Carlo error is reduced to acceptable levels,
these types of problem remain frustratingly out of our grasp.

Many advances have been made in the field of MCMC, to design ever more
complex methods, which more intelligently propose moves which leads to
faster converging methods. Function space versions of standard methods
such as the random walk Metropolis-Hastings (RWMH) algorithm or the
Metropolis adjusted Langevin algorithm (MALA), whose convergence rates
are independent of dimension have been
developed\cite{cotter2013mcmc}. The hybrid (or Hamiltonian) Monte
Carlo (HMC) method uses Hamiltonian dynamics in order to propose and
accept moves to states which are a long way away from the current
position\cite{sexton1992hamiltonian}, and function space analogues of
this have also been proposed\cite{beskos2011hybrid}. Riemann
manifold Monte Carlo methods exploit the Riemann geometry of the
parameter space, and are able to take advantage of the local structure
of the target density to produce more efficient MCMC
proposals\cite{girolami2011riemann}. This methodology has been
successfully applied to MALA-type proposals and methods which exploit
even higher order gradient information\cite{bui2014solving}.  These
methods allow us to more fully explore the posterior distribution, at
the cost of fewer iterations of the method.

Simultaneously, great strides are continually being made in the
development of computing hardware. Moore's law, which predicted that
the number of transistors that it is possible to fit on a single
microchip will double every two years, has been largely followed
since the early 70s\cite{moore1998cramming}. However, the main revolution with regards to
scientific computing in recent decades has been the increasing focus on parallel
architectures. The efficient exploitation of these facilities is the key to
solving many of the computational challenges that we currently face.

@@

In this paper, we present a framework for parallelisation of
importance sampling, which allows us to use any of the current
Metropolis-based methodologies in order to create an efficient target
proposal from the current state of all of the chains in the
ensemble. In Section \ref{Sec:Prelim} we outline some preliminaries,
including the general set up for Bayesian inverse problems, the
preconditioned Crank-Nicolson Langevin (pCNL) algorithm and a
brief review of the optimal transport resampler,  both of which we will be
employing within the algorithm. We describe the Parallel Adaptive
Importance Sampler (PAIS) in Section \ref{Sec:PAIS}, and in Section
\ref{Sec:adapt} we describe how algorithmic parameters can be
automatically tuned to provide optimal convergence. In
Section \ref{Sec:Num}, we present some numerical experiments which
demonstrate the savings that can be made by employing this approach as
opposed to a naive/trivial parallelisation of existing MCMC
methods. In Section \ref{Sec:Conc}, we will summarise our results and
suggest some areas for future investigation.

\section{Preliminaries}\label{Sec:Prelim}
In this Section we will introduce preliminary topics and algorithms
that will be referred to throughout the paper.
\subsection{Bayesian inverse problems}
In this paper, we particularly focus on the use of MCMC methods in characterising
posterior probability distributions in Bayesian inverse problems. We
wish to learn about a particular unknown quantity $u$, of which we are
able to make direct or indirect noisy observations. For now
we say that $u$ is a member of a Hilbert
space $X$.

The parameter $u$ is observed
through the observation operator $\mathcal{G}:X \to
\mathbb{R}^d$. Since observations are rarely, if ever, perfect, we
assume that these measurements $\data$ are subject to Gaussian noise, so that
\begin{equation}\label{eqn:obs}
	\data = \mathcal{G}(u) + \varepsilon, \qquad \varepsilon \sim \mu_{\varepsilon} = \mathcal{N}(0,\Sigma).
\end{equation}
For example, if $u$ are the rates of reactions in a chemical system, $\G$ might return the times at which each reaction occurs, or some summary of this information.

@@

The Ensemble Transform (ET) method proposed by Reich \cite{reich2013nonparametric} makes use of optimal transportation as described in \cite{villani2003topics,villani2008optimal}. The transform takes a sample of weighted particles $\{y_i\}_{i=1}^M$ from $\mu_Y$ and converts it into a sample of evenly weighted particles $\{x_i\}_{i=1}^M$ from $\mu_X$, by means of defining a coupling $T^*$ between $Y$ and $X$. Given that a trivial coupling $T^t$ always exists in the space of transference plans, $\Pi(\mu_{X}, \mu_{Y})$, we can find a coupling $T^*$ which maximises the correlation between $X$ and $Y$ \cite{cotter2012ensemble}. This coupling is the solution to a linear programming problem in $M^2$ variables with $2M-1$ constraints as defined in \cite{reich2013nonparametric}. Maximising the correlation ensures that the new sample is as much like the original sample as possible with the additional property that the sample is evenly weighted.

As proposed in \cite{reich2013nonparametric} a Monte Carlo algorithm can be implemented to resample from a weighted ensemble. We create a weighted sample, then solve the optimal transport problem which produces the coupling described above, we can draw a new sample from the evenly weighted distribution. Reich suggests using the mean of the evenly weighted distribution to produce a consistent estimator.

@@

\begin{table}
\begin{mdframed}
\begin{algorithmic}
\STATE $\X^{(0)} = \X_0 = [x_1^{(0)},x_2^{(0)},\ldots,x_M^{(0)}]^T$
\FOR{$i=0,1,2, ..., N$}
\STATE $\Y^{(i)} = [y_1^{(i)},y_2^{(i)},\ldots,y_M^{(i)}]^T, \quad y_j^{(i)} \sim
\nu(\cdot;x_j^{(i)})$
\STATE $\chi(y;\X^{(i)}) = \frac{1}{M}
\sum_{j=1}^M \nu(y;x_j^{(i)})$.
\STATE $\W^{(i)} = [w_1^{(i)},w_2^{(i)},\ldots,w_M^{(i)}]^T,$ \quad $w^{(i)}_j =
\frac{\pi(y_j^{(i)})}{\chi(y_j^{(i)};\X^{(i)})}$.
\STATE Resample: $(\W^{(i)},\Y^{(i)}) \rightarrow (\frac{1}{M}\mathbf{1}, \X^{(i+1)})$
\ENDFOR 
\end{algorithmic}
\end{mdframed}

@@

Efficient selection of scaling parameters in MCMC algorithms is critical to achieving optimal mixing rates and hence achieving fast convergence to the target density. One significant difficulty is finding an appropriate $\nu$ such that
$\chi$ is a close approximation to the posterior density $\pi$. If the proposal distribution is too over-dispersed, then the algorithm will propose states a long way from the current state but there will be a relatively low acceptance rate, impacting the quality of inferences on the posterior. Similarly, if the posterior is under-dispersed, the process will take a long time to fully explore the space so the mixing rate, and hence convergence rate, will be slow. It is therefore necessary to find a proposal distribution which is slightly over-dispersed to ensure the entire posterior is explored\cite{gelman1992inference}, but is as close to the posterior as possible.

@@

MCMC algorithms can be assessed by comparing their approximation of the posterior to the analytic distribution. To assess this, a distance metric must be decided on, such as the relative error between the sample moments and the true moments, or the relative L2 error between the true density, $\pi(x|D)$, and the constructed histogram. The relative error in the $m$-th moment is
\[
	\left|\frac{N^{-1}\sum_{i=1}^N \! x_i^m - \mathbb{E}[X^m]}{\mathbb{E}[X^m]}\right|,
\]
where $\{x_i\}_{i=1}^N$ is a sample of size $N$ produced by the algorithm. The relative L2 error between a continuous function to a piecewise constant function, $e$, is
\begin{equation}\label{eqn:L2_error}
	e^2 = \sum\limits_{i=1}^{n_b}\left[\displaystyle\int_{R_i} \! \pi(a|D) \, \mbox{d}a - vB_i\right]^2 \Big/ \sum\limits_{i=1}^{n_b}\left[\displaystyle\int_{R_i} \! \pi(a|D) \, \mbox{d}a\right]^2,
\end{equation}
where the points $\{R_i\}_{i=1}^{n_b}$ are the $d$-dimensional regions the histogram is defined over, so that $\bigcup_i R_i \subseteq X$ and $R_i\cap R_j=\emptyset$, $n_b$ is the number of bins, $v$ is the volume of a bin, and $B_i$ is the value of the $i$th bin.

@@

The effective sample size can be defined in the following way:
\[
	\neff = \frac{\left(\sum_{i=1}^M \! w_i\right)^2}{\sum_{i=1}^M \! w_i^2} \approx \frac{M\E(w)^2}{\E(w^2)} = M\left(1 - \frac{\mbox{var}(w)}{\mathbb{E}(w^2)}\right).
\]
The second two expressions are true when $M\rightarrow\infty$. From
the last expression we see that when the variance of the weights is
zero, $\neff = M$, which is our ideal scenario. In a neighbourhood around $\delta_{\text{var}}^*$, $\neff$ decreases, when the variance increases. So if $v(w(y))$ can be equal to zero for a particular problem and proposal distribution, maximising the effective sample size is equivalent to minimising the variance of the weights. In the PAIS algorithm we have a dynamic proposal which is perturbed at every iteration.

@@

In this section we investigate the behaviour of the PAIS algorithm
when applied to bimodal problems. Metropolis-Hastings methods can
struggle with multimodal problems, particularly where switches between
the modes are rare, resulting incorrectly proportioned modes in the
histograms produced. With the PAIS algorithm, we see that the
resampling step allows redistribute chains to new modes as they are
found. This means that we expect the number of chains in a mode to be
approximately proportional to the probability mass in that mode. As a result, reconstructed posteriors with disproportional modes, as is familiar with the Metropolis-Hastings algorithms, are not produced. We again look at an `easy' problem, BM(1), which has a KL divergence of 0.880, and a `harder' problem, BM(2), which has a KL divergence of 3.647. Problem BM(1) has two modes which are separated by a smaller energy barrier. In BM(2) we increase the distance between the two modes which has the effect of increasing the required energy to jump between modes. These posteriors are shown in Figure~\ref{fig:problem 3 posteriors}.

@@

We have explored the application of parallelised MCMC algorithms in
low dimensional Inverse problems. We have demonstrated numerically
that these algorithms converge faster than the analogous naively parallelised
Metropolis-Hastings algorithms. Further experimentation with the
Random Walk Metropolis-Hastings (RWMH), Metropolis Adjusted Langevin
Algorithm (MALA) and preconditioned Crank-Nicolson (pCN) proposals has
yielded similar results\cite{Paul}.%  Importantly, we have demonstrated
% that the convergence rate improves superlinearly with respect to the
% number of processors used.

>>>>

\newcommand{\picturesAB}[6]{
\centerline{
\hskip #4
\raise #3 \hbox{\raise 0.9mm \hbox{(a)}}
\hskip #5
\epsfig{file=#1,height=#3}
\hskip #6
\raise #3 \hbox{\raise 0.9mm \hbox{(b)}}
\hskip #5
\epsfig{file=#2,height=#3}
}}
\newcommand{\picturesCD}[6]{
\centerline{
\hskip #4
\raise #3 \hbox{\raise 0.9mm \hbox{(c)}}
\hskip #5
\epsfig{file=#1,height=#3}
\hskip #6
\raise #3 \hbox{\raise 0.9mm \hbox{(d)}}
\hskip #5
\epsfig{file=#2,height=#3}
}}
\author{Colin Cotter\thanks{Department of Mathematics, Imperial
    College, London, UK} \and Simon Cotter\thanks{School of
    Mathematics, University of Manchester, Manchester, UK. e: simon.cotter@manchester.ac.uk} \and Paul Russell\thanks{School of
    Mathematics, University of Manchester, Manchester, UK}}
\title{Parallel Adaptive Importance Sampling}
\begin{document}
\maketitle
\begin{abstract}
  Markov chain Monte Carlo methods are a powerful and commonly used
  family of numerical methods for sampling from complex probability
  distributions. As applications of these methods increase in size and complexity, the need for efficient
  methods which can exploit the parallel architectures which are
  prevalent in high performance computing increases. In this paper, we
  aim to develop a framework for scalable parallel MCMC algorithms. At
  each iteration, an importance sampling proposal distribution is
  formed using the current states of all of the chains within an
  ensemble. Once weighted samples have been produced from this, a
  state-of-the-art resampling method is then used to create an evenly
  weighted sample ready for the next iteration. We demonstrate that
  this parallel adaptive importance sampling (PAIS) method outperforms
  naive parallelisation of serial MCMC methods using the same number
  of processors, for low dimensional problems, and in fact shows
  better than linear improvements in convergence rates with respect to
  the number of processors used.
\end{abstract}
\begin{keywords}MCMC, parallel, importance sampling, Bayesian, inverse problems.
\end{keywords}
\section{Introduction}
%\subsection{Lit. review}
%\subsection{Optimal transport resampler}
%\subsection{Function Space MCMC}
Markov chain Monte Carlo (MCMC) methods are a powerful family of tools
that allow us to sample from complex probability distributions. MCMC
methods were first developed in the 70s\cite{hastings1970monte}, and with the development of
to use MCMC methods for many more. In particular, when
considering Bayesian inverse problems, each MCMC step may involve the
numerical solution of one or more PDE. As many samples are usually
required before Monte Carlo error is reduced to acceptable levels,
these types of problem remain frustratingly out of our grasp.

Many advances have been made in the field of MCMC to design ever more
complex methods that propose moves more intelligently, leading to
rapidly converging methods. Function space versions of standard methods
such as the random walk Metropolis-Hastings (RWMH) algorithm or the
Metropolis adjusted Langevin algorithm (MALA), whose convergence rates
are independent of dimension have been
developed\cite{cotter2013mcmc}. The hybrid (or Hamiltonian) Monte
Carlo (HMC) method uses Hamiltonian dynamics in order to propose and
accept moves to states which are a long way away from the current
position\cite{sexton1992hamiltonian}, and function space analogues of
this have also been proposed\cite{beskos2011hybrid}. Riemann
manifold Monte Carlo methods exploit the Riemann geometry of the
parameter space, and are able to take advantage of the local structure
of the target density to produce more efficient MCMC
proposals\cite{girolami2011riemann}. This methodology has been
successfully applied to MALA-type proposals and methods which exploit
even higher order gradient information\cite{bui2014solving}.  These
methods allow us explore the posterior distribution more fully 
with fewer iterations.

Simultaneously, great strides are continually being made in the
development of computing hardware. Moore's law, which predicted that
the number of transistors that can to fit on a single microchip will
double every two years, has been largely followed since the early
70s\cite{moore1998cramming}. In recent times, it has become necessary
to use parallel architectures to exploit Moore's law. The efficient
exploitation of these facilities is the key to solving many of the
computational challenges that we currently face.

@@

In this paper, we present a framework for parallelisation of
importance sampling, which can be built around any of the current
Metropolis-based methodologies in order to create an efficient target
proposal from the current state of all of the chains in the
ensemble. The idea is to consider the parallel chains as an ensemble,
and to resample using a transformation based on optimal transport.
Samplers based on optimal transport have also been considered in
\cite{el2012bayesian}.

In Section \ref{Sec:Prelim} we outline some preliminaries,
including the general set up for Bayesian inverse problems, the
preconditioned Crank-Nicolson Langevin (pCNL) algorithm and a
brief review of the optimal transport resampler,  both of which we will be
employing within the algorithm. We describe the Parallel Adaptive
Importance Sampler (PAIS) in Section \ref{Sec:PAIS}, and in Section
\ref{Sec:adapt} we describe how algorithmic parameters can be
automatically tuned to provide optimal convergence. In
Section \ref{Sec:Num}, we present some numerical experiments that
demonstrate the savings available by employing this approach as
opposed to a naive/trivial parallelisation of existing MCMC
methods. In Section \ref{Sec:Conc}, we summarise our results and
suggest some areas for future investigation.

\section{Preliminaries}\label{Sec:Prelim}
In this Section we will introduce preliminary topics and algorithms
that will be referred to throughout the paper.
\subsection{Bayesian inverse problems}
In this paper, we focus on the use of MCMC methods for characterising
posterior probability distributions in Bayesian inverse problems. We
wish to learn about a particular unknown quantity $u$, of which we are
able to make direct or indirect noisy observations. For now
we say that $u$ is a member of a Hilbert
space $X$.

The parameter $u$ is observed
through the observation operator $\mathcal{G}:X \to\mathbb{R}^d$. 
Since observations are never perfect, we
assume that these measurements $\data$ are subject to Gaussian noise, so that
\begin{equation}\label{eqn:obs}
	\data = \mathcal{G}(u) + \varepsilon, \qquad \varepsilon \sim \mu_{\varepsilon} = \mathcal{N}(0,\Sigma).
\end{equation}
For example, if $u$ are the rates of reactions in a chemical system, $\G$ might return the times at which each reaction occurs, or some summary of this information.

@@

The Ensemble Transform (ET) method proposed by Reich \cite{reich2013nonparametric} makes use of optimal transportation as described in \cite{villani2003topics,villani2008optimal}. The transform takes a sample of weighted particles $\{y_i\}_{i=1}^M$ from $\mu_Y$ and converts it into a sample of evenly weighted particles $\{x_i\}_{i=1}^M$ from $\mu_X$, by means of defining a coupling $T^*$ between $Y$ and $X$. Given that a trivial coupling $T^t$ always exists in the space of transference plans, $\Pi(\mu_{X}, \mu_{Y})$, we can find a coupling $T^*$ which maximises the correlation between $X$ and $Y$ \cite{cotter2012ensemble}. This coupling is the solution to a linear programming problem in $M^2$ variables with $2M-1$ constraints. Maximising the correlation ensures that the new sample is as much like the original sample as possible with the additional property that the sample is evenly weighted.

A Monte Carlo algorithm can be implemented to resample from a weighted ensemble. We create a weighted sample, then solve the optimal transport problem which produces the coupling described above, we can draw a new sample from the evenly weighted distribution. Reich suggests using the mean of the evenly weighted distribution to produce a consistent estimator.

@@

\begin{table}
\begin{mdframed}
\begin{algorithmic}
\STATE $\X^{(0)} = \X_0 = [x_1^{(0)},x_2^{(0)},\ldots,x_M^{(0)}]^T$
\FOR{$i=0,1,2, ..., N$}
\STATE $\Y^{(i)} = [y_1^{(i)},y_2^{(i)},\ldots,y_M^{(i)}]^T, \quad y_j^{(i)} \sim
\nu(\cdot;x_j^{(i)})$
\STATE $\chi(y;\X^{(i)}) = \frac{1}{M}
\sum_{j=1}^M \nu(y;x_j^{(i)})$.
\STATE $\W^{(i)} = [w_1^{(i)},w_2^{(i)},\ldots,w_M^{(i)}]^T,$ \quad $w^{(i)}_j =
\frac{\pi(y_j^{(i)})}{\chi(y_j^{(i)};\X^{(i)})}$.
\STATE Resample using ETMC: $(\W^{(i)},\Y^{(i)}) \rightarrow (\frac{1}{M}\mathbf{1}, \X^{(i+1)})$
\ENDFOR 
\end{algorithmic}
\end{mdframed}

@@

Efficient selection of scaling parameters in MCMC algorithms is critical to achieving optimal mixing rates and hence achieving fast convergence to the target density. One significant difficulty is finding an appropriate $\nu$ such that
$\chi$ is a close approximation to the posterior density $\pi$. If the proposal distribution is over-dispersed, then the algorithm will propose states a long way from the current state at the cost of a relatively low acceptance rate, impacting the quality of inferences on the posterior. Similarly, if the posterior is under-dispersed, the process will take a long time to fully explore the space so the mixing rate, and hence convergence rate, will be slow. It is therefore necessary to find a proposal distribution which is slightly over-dispersed to ensure the entire posterior is explored\cite{gelman1992inference}, but is as close to the posterior as possible.

@@

MCMC algorithms can be assessed by comparing their approximation of the posterior to the analytic distribution. To assess this, a distance metric must be chosen. Examples are the relative error between the sample moments and the true moments, or the relative L2 error between the true density, $\pi(x|D)$, and the constructed histogram. The relative error in the $m$-th moment is
\[
	\left|\frac{N^{-1}\sum_{i=1}^N \! x_i^m - \mathbb{E}[X^m]}{\mathbb{E}[X^m]}\right|,
\]
where $\{x_i\}_{i=1}^N$ is a sample of size $N$ produced by the algorithm. The relative L2 error between a continuous function to a piecewise constant function, $e$, is
\begin{equation}\label{eqn:L2_error}
	e^2 = \sum\limits_{i=1}^{n_b}\left[\displaystyle\int_{R_i} \! \pi(a|D) \, \mbox{d}a - vB_i\right]^2 \Big/ \sum\limits_{i=1}^{n_b}\left[\displaystyle\int_{R_i} \! \pi(a|D) \, \mbox{d}a\right]^2,
\end{equation}
where the points $\{R_i\}_{i=1}^{n_b}$ are the $d$-dimensional histogram bins, so that $\bigcup_i R_i \subseteq X$ and $R_i\cap R_j=\emptyset$, $n_b$ is the number of bins, $v$ is the volume of a bin, and $B_i$ is the value of the $i$th bin.

@@

The effective sample size can be defined in the following way:
\[
	\neff = \frac{\left(\sum_{i=1}^M \! w_i\right)^2}{\sum_{i=1}^M \! w_i^2} \approx \frac{M\E(w)^2}{\E(w^2)} = M\left(1 - \frac{\mbox{var}(w)}{\mathbb{E}(w^2)}\right).
\]
The second two expressions are true when $M\rightarrow\infty$. From
the last expression we see that when the variance of the weights is
zero, $\neff = M$; this is our ideal scenario. In a neighbourhood around $\delta_{\text{var}}^*$, $\neff$ decreases when the variance increases. So if $v(w(y))$ can be equal to zero for a particular problem and proposal distribution, maximising the effective sample size is equivalent to minimising the variance of the weights. In the PAIS algorithm we have a dynamic proposal which is perturbed at every iteration.

@@

In this section we investigate the behaviour of the PAIS algorithm
when applied to bimodal problems. Metropolis-Hastings methods can
struggle with multimodal problems, particularly where switches between
the modes are rare, resulting in incorrectly proportioned modes in the
histograms, for example. With the PAIS algorithm, we see that the
resampling step redistributes chains to new modes as they are
found. This means that we expect the number of chains in a mode to be
approximately proportional to the probability mass in that mode. As a result, reconstructed posteriors with disproportional modes, as is familiar with the Metropolis-Hastings algorithms, are not produced. We again look at an `easy' problem, BM(1), which has a KL divergence of 0.880, and a `harder' problem, BM(2), which has a KL divergence of 3.647. Problem BM(1) has two modes which are separated by a smaller energy barrier. In BM(2) we increase the distance between the two modes which has the effect of increasing the required energy to jump between modes. These posteriors are shown in Figure~\ref{fig:problem 3 posteriors}.

@@

We have explored the application of parallelised MCMC algorithms in
low dimensional inverse problems. We have demonstrated numerically
that these algorithms converge faster than the analogous naively parallelised
Metropolis-Hastings algorithms. Further experimentation with the
Random Walk Metropolis-Hastings (RWMH), Metropolis Adjusted Langevin
Algorithm (MALA) and preconditioned Crank-Nicolson (pCN) proposals has
yielded similar results\cite{Paul}.%  Importantly, we have demonstrated
% that the convergence rate improves superlinearly with respect to the
% number of processors used.
